\documentclass[12pt, letterpaper]{article} 
\usepackage{tabularx} % Advanced table configurations
\usepackage[utf8]{inputenc}
\usepackage[left=2cm,right=2cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{indentfirst}
\usepackage{array,multirow}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{sectsty}
\usepackage{float}
\usepackage{graphicx}
\usepackage{picture}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{mathptmx}
\usepackage{setspace}
\usepackage{adjustbox}
\usepackage[caption = false]{subfig}
\usepackage[flushleft]{threeparttable}
\usepackage{makecell}
\usepackage{bm}
\usepackage[font=bf]{caption}
\usepackage{cancel}
\usepackage{anyfontsize}
\usepackage{etoolbox}
\usepackage{amssymb}
\usepackage{pdfpages}
\usepackage{booktabs}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{lmodern}
\usepackage{footnote}
\usepackage[bottom]{footmisc}
\usepackage[citecolor=blue]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    }
\definecolor{UBCblue}{rgb}{0.04706, 0.13725, 0.32}
%\subsectionfont{\color{UBCblue}}
\subsectionfont{\fontsize{12}{15}\selectfont}
\sectionfont{\fontsize{14}{18}\selectfont}
\allsectionsfont{\mdseries\scshape}
\makesavenoteenv{tabular}

\begin{document} 

\begin{center}
{\Huge \textsc{Nicolás Urdaneta}}
\vspace*{5mm}

\begin{tabular}{@{}m{6.75cm}m{6.75cm}m{5.2cm}}
\noindent n.urdaneta@duke.edu & \href{nicolasurdaneta.github.io}{nicolasurdaneta.github.io} & (+1) 217-9795876 \\
Last updated: July 2023
\end{tabular}
\vspace*{-7mm}

\end{center}
\section*{Profile}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}
\noindent I am an economics PhD student at Duke University. I previously worked as research assistant at the Economics Faculty at Universidad de Los Andes, Colombia, working for Marcela Eslava on firm dynamics, productivity, and market power. I hold a M.A and a B.A. in economics from Universidad de Los Andes. I am primarily interested in approaching problems through empirical work with structural models. My current research interests are in firm dynamics, innovation, trade, market power, economic development, and applied econometrics. I also work on other projects on internal migration and displacement in Colombia and gender bias in student evaluations of teaching. 

\vspace*{-4mm}

\section*{Education}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}
\noindent
Ph.D. Economics, \textbf{Duke Univeristy}. \hfill 2022 - Present \\
M.A. Economics, \textbf{Universidad de los Andes} - Colombia (\textit{cum laude}). \hfill 2019 - 2021 \\
B.A. Economics, \textbf{Universidad de los Andes} - Colombia (\textit{cum laude}). \hfill 2015 - 2019

\vspace*{-2mm}

\section*{Published papers}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}
\noindent The Size and Life-Cycle Growth of Plants: The Role of Productivity, Demand, and Wedges. (2023). \textit{The Review of Economic Studies}.   With \textit{Marcela Eslava and John Haltiwanger}. Document available \href{https://academic.oup.com/restud/advance-article/doi/10.1093/restud/rdad029/7054272?login=true}{here}. 

\vspace*{-4mm}

\section*{Working papers}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}

\noindent Market Concentration, Market Fragmentation, and Inequality in Latin America. (2021). UNDP LAC Working Paper No. 11. Background Paper for the UNDP LAC Regional Human Development Report 2021.  With \textit{Marcela Eslava} and \textit{Marcela Meléndez}. Working paper available \href{https://www.latinamerica.undp.org/content/rblac/en/home/library/poverty/market-concentration--market-fragmentation--and-inequality-in-la.html}{here}. \\ [-3mm]

\noindent ``Talented'' Men and ``Kind'' Women? Gender Bias in Student Evaluations of Teaching. (2021). Documento CEDE No. 46. (Master's thesis). Document available \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3919797}{here}. In the media: \href{https://www.elespectador.com/educacion/los-profes-crack-y-las-profes-amables-el-sesgo-de-genero-en-las-aulas/}{El Espectador}.

\vspace{-5mm}

\section*{Work in progress}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}
\noindent Equilibrium Gender Discrimination in Student Evaluation of Teaching. With \textit{Sara Ayllon, Lars Lefgren, Richard Patterson, and Olga Stoddard}. \\ [-3mm]

\noindent Reconciling the Effects of Migration: Do the Opportunity Costs Shape the Local Effects?. With \textit{Mateo Arbeláez and Juan Sebastián Muñoz}. \\ [-3mm]

\vspace{-6mm}

\section*{Research Experience}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}
\noindent
Research Assistant for Marcela Eslava, Full-Professor and Economics Dean, Universidad de Los Andes. Main research projects joint with John Haltiwanger and Marcela Meléndez (Jun. 2019 - Jul. 2022).  \\ 

\newpage

\section*{Teaching Experience}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}
\vspace*{-12mm}
\subsubsection*{Graduate Teacher Assistant - Universidad de Los Andes}
\vspace*{-1mm}
\noindent
Impact Evaluation for Public Policy (\textit{prof. Adriana Camacho}) \hfill 2020 II \\
Intermediate Econometrics (\textit{prof. Mateo Arbeláez}) \hfill 2020 Summer \\
World Economic History (\small{\textit{prof. Leopoldo Fergusson and Juan Sebastián Galán}})  \hfill  2020 I  \\
Intermediate Macroeconomics (\textit{prof. David Pérez and Andrés Zambrano}) \hfill 2019 II \& 2020 I \\

\vspace*{-7mm}
\subsubsection*{Undergraduate Teacher Assistant - Universidad de Los Andes}
\vspace*{-1mm}
\noindent
Monetary Policy and Theory \hfill 2018 II \& 2019 I \\
Intermediate Econometrics \hfill 2018 Summer  \\
Intermediate Microeconomics \hfill 2017 Summer \\
Mathematical Methods for Economics \hfill 2017 II \\ 
Study hall for Calculus 3, Integral Calculus, Linear Algebra, and Differential Calculus. \hfill 2017 I \\
Integral Calculus \hfill  2016 II

\vspace*{-4mm}

\section*{Awards}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}
\noindent
Sixth place National Colombian Mathematical Olympics 30th Edition. First level category. \hfill 2011 \\ [1mm]
Noche de los mejores. One of the best results in the Colombian higher education examinations  \newline (Saber-Pro). The award was given to 1,324 graduates out of over 240,000. \hfill 2019 \\
\vspace{-8mm}

\section*{Other experience}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}
\noindent
Supuestos Economics Magazine (2016 - 2019). This is the economics student's magazine from Universidad de Los Andes. I held multiple roles: Editorial Director (2019), Revision and Edition Sub Director (2018), Communications Sub Director (2017 II). Six publications in printed edition, including two main articles. Link to \href{https://revistasupuestos.com/}{website} (in Spanish).

\vspace{-4mm}

\section*{Skills}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}
\noindent
\begin{tabular}{@{}p{3.5cm}p{5cm}p{3.5cm}p{3.7cm}}
Stata, R \& Latex &  Advanced & Python \& Julia &  Basic \\
\end{tabular}

\vspace{-4mm}

\section*{Languages}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}
\noindent
\begin{tabular}{@{}p{3.5cm}p{5cm}p{3.5cm}p{3.7cm}}
English & Fluent	&  Spanish & Native Language \\
\end{tabular}

\vspace{-4mm}

\section*{References}
\vspace*{-8mm}
\noindent \rule{\linewidth}{0.2mm}
\noindent
\begin{tabular}{@{}p{3.5cm}p{13.7cm}}
\\ [-3mm]
Marcela Eslava & Full Professor and Economics Dean, Universidad de Los Andes. meslava@uniandes.edu.co \\ [8mm]
John Haltiwanger & Distinguished University Professor, University of Maryland. halt@umd.edu \\ [4mm]
Adriana Camacho	& Associate Professor, Universidad de Los Andes. adcamach@uniandes.edu.co
\\ [4mm]
Lars Lefgren & Department Chair and Professor, Bringham Young University. lars\_lefgren@byu.edu
\end{tabular}
\end{document}


